Thesis plan\\Version 1.0

### 2018-04-16 Thesis plan/Thesis plan.tex
updated thesis plan

\subitem{Which parameter values create embeddings with the highest accuracy for academic texts?}

@@

\section{Research method}
\subsection{Method \& Validation}
\paragraph{Method} To answer the stated research questions, a fitted approach must be applied. For this project, the research method '\textit{Controlled Experiments}' will be applied. Using this methodology, the goal of this project is to validate these two hypothesis:
\begin{itemize}
\item{The word-to-vec embedding method can have an higher accuracy for academic texts than the TF-IDF algorithm.}
\item{The accuracy of academic embedding methods can be validated using classification tasks}
\end{itemize}
\paragraph{Validation} This research will be validated via a clear presentation of all compared results. The usage of a publicly available collection and via a clear presentation of the used parameters for each method.

@@

\section{Expected project results}
This research results in the following findings:
\begin{itemize}
\item{Comparison of multiple embedding methods for a collection of academic texts}
\subitem{- If possible, a best-to-use method}
\item{Validation of the hypothesis 'The accuracy of embedding methods is related to the type of text.'}
\subitem{- If these are related, an analysis of relationship in accuracy of the methods for the academic and non-academic texts.}
\end{itemize}
\section{Required expertise for this project}
This project requires:
\begin{itemize}
\item{Basic understanding of Machine Learning}
\item{Knowledge of Databricks/Spark (AWS)}
\item{Knowledge of embedding (methods \& evaluation)}
\item{SQL programming}
\item{Python programming}
\end{itemize}
\section{Timeline}
\begin{center}
\begin{tabular}{lll}
\textbf{Focus} & \textbf{Number of weeks} & \textbf{Date} \\
Setting up workspace & 1 & April 3 - April 6\\
Implementing methods & 2 & April 9 - April 20\\
Finding optimal & 3 & April 23 - May 11\\
embedding parameters & & \\
Data gathering experiment 1 & 1 & May 14 - May 18\\
Data gathering experiment 2 & 1 & May 21 - May 25\\
Writing & 2 & May 28 - June 8\\
Correction & 1 & June 11 - June 15\\
Submission & 1 & June 18 - June 22\\
Total & 12 & presentation date (NOT YET CONFIRMED) July 10\\
\end{tabular}\\
\end{center}
*  for non-academic texts\\ ** for academic texts

>>>>

\item{Which parameter values create embeddings with the highest accuracy for academic texts?}

@@

\section{Research method}
\subsection{Method \& Validation}
\paragraph{Method} To answer the stated research questions, a fitted approach must be applied. For this project, the research method '\textit{Controlled Experiments}' will be applied. Using this methodology, the goal of this project is to validate these two hypothesis:
\begin{itemize}
\item{The word-to-vec embedding method can have an higher accuracy or more utility\footnote{as in, reduced storing capacity and scalability to document/journal level} for academic texts than the TF-IDF algorithm.}
\item{The accuracy of academic embedding methods can be validated using classification tasks}
\end{itemize}
\paragraph{Validation} This research will be validated via a clear presentation of all compared results. The usage of a publicly available collection and via a clear presentation of the used parameters for each method.

@@

\section{Expected project results}
This research results in the following findings:
\begin{itemize}
\item{Comparison of multiple embedding validation methods for a collection of academic texts}
\subitem{- If possible, a best-to-use method}
\item{Validation of the hypothesis 'The word-to-vec embedding method can have an higher accuracy for academic texts than the TF-IDF algorithm.'}
\subitem{- If these are related, an analysis of relationship in accuracy of the methods for the academic and non-academic texts.}
\end{itemize}
\section{Required expertise for this project}
This project requires:
\begin{itemize}
\item{Basic understanding of Machine Learning}
\item{Knowledge of Databricks/Spark (AWS)}
\item{Knowledge of embedding (methods \& evaluation)}
\item{SQL programming}
\item{Python programming}
\end{itemize}
\section{Timeline}
\begin{center}
\begin{tabular}{lll}
\textbf{Focus} & \textbf{Number of weeks} & \textbf{Date} \\
Setting up workspace & 1 & April 3 - April 6\\
Implementing methods & 2 & April 9 - April 20\\
Finding optimal & 3 & April 23 - May 11\\
embedding parameters & & \\
Data gathering experiment 1 & 1 & May 14 - May 18\\
Data gathering experiment 2 & 1 & May 21 - May 25\\
Writing & 2 & May 28 - June 8\\
Correction & 1 & June 11 - June 15\\
Submission & 1 & June 18 - June 22\\
Total & 12 & presentation date (NOT YET CONFIRMED) July 10\\
\end{tabular}\\
\end{center}
*  for non-academic texts\\ ** for academic texts
